Complex Analysis of Askaryan Radiation: UHE-$\nu$ Energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-08-07 template.tex
minor work on abstract and intro

\begin{abstract}
This is a work in progress.
\end{abstract}

@@

The introduction.

>>>>

\begin{abstract}
The detection of neutrinos with energies greater than 10 PeV has been a long-time goal of the astroparticle physics community.  A key strategy has been to deploy autonomous, radio-frequency (RF) detetectors in polar regions that rely on the Askaryan effect in ice for the neutrino signal.  The Askaryan effect occurs when the excess negative charge within a high-energy cascade radiates in a dense medium.  Neutrinos with energies above 10 PeV can induce cascades that radiate in the radio-frequency (RF) bandwidth above thermal backgrounds.  To identify neutrino signals in future data from Askaryan-class detectors, analytic models of the Askaryan electromagnetic field have been created and compared to simulations and laboratory measurements.  In the past, these models have only described the Askaryan electromagnetic field, leaving the effect of the RF detection channels on the field to simulation packages.  In this work, we present a fully analytic Askaryan model that accounts for the effect of an RF detection channel.  We provide formulas for the observed voltage trace, and for the Hilbert envelope of the trace.  We compare our analytic envelope equation to simulated data computed with NuRadioMC, a key Monte Carlo toolset in high-energy neutrino detection.  Our equation matches the data with correlation coefficients greater than 0.95.  Using the analytic envelope technique, we reconstruct key neutrino properties.
\end{abstract}

@@

Cosmic neutrinos with energies up to 100 PeV have been detected by the IceCube and KM3NeT collaborations \cite{10.1126/science.1242856,aartsen2013first-bff,collaboration2016observation-03b,collaboration2018neutrino-2a0,collaboration2021detection-6fa,collaboration2022evidence-a08,collaboration2023observation-08b,collaboration2025observation-22f}. Previous analyses indicate that the discovery of neutrinos above 5 PeV to 20 EeV will  require large Askaryan-class detectors \cite{10.1103/physrevd.98.062003}.  Neutrinos with energies in the EeV range could potentially reveal the source of ultra-high energy cosmic rays.  Further, studying electroweak interactions at these energies is virtually impossible on Earth, and Askaryan-class neutrino detectors could provide new data.

%of ultra-high-energy neutrinos (UHE-ν) will require an
%expansion in detector volume because the flux is expected
%to decrease with energy [2–6]. The UHE-ν flux could
%potentially explain the origin of UHE cosmic rays
%(UHECR), and provides the opportunity to study electro-
%weak interactions at record-breaking energies [7,8].
%Utilizing the Askaryan effect expands the effective volume
%of UHE-ν detector designs, because this effect offers a way
%to detect UHE-ν with radio pulses that travel more than
%1 km in sufficiently RF-transparent media such as Antarctic
%and Greenlandic ice [9–11].
